% Kyle O'Sullivan - CS Resume
\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

% Formatting
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*,nosep,topsep=2pt}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{KYLE O'SULLIVAN}}\\[4pt]
    \href{https://linkedin.com/in/kos33/}{linkedin.com/in/kos33/} , \href{https://github.com/kylezinho}{github.com/kylezinho}\\
    \href{mailto:kos33@bath.ac.uk}{kos33@bath.ac.uk} , 07305403957
\end{center}

% Education
\section*{EDUCATION}

\textbf{University of Bath}, Bath, UK \hfill \textit{2025 Sep-2026 Sep}\\
\textit{MSc Computer Science (Awarded £15,000 in Scholarships)}
\begin{itemize}
    \item Software Development, Software Engineering, Artificial Intelligence and Machine Learning
\end{itemize}

\textit{BSc Management (First)} \hfill \textit{2022 Sep-2025 July}
\begin{itemize}
    \item \#1 cohort Business Analytics, \#1 for Strategy with AI, \#5 for Finance
\end{itemize}

\textbf{Yonsei University}, Seoul, South Korea \hfill \textit{2023 Jun-2023 Aug}\\
\textit{Exchange in Venture Capital and Entrepreneurship (Grade A)}
\begin{itemize}
    \item Developed a deep understanding of venture capital and the underpinnings of Series-A funding
\end{itemize}

\textbf{Nanyang Technological University}, Singapore \hfill \textit{2022 Jun-2022 Aug}\\
\textit{Exchange in Human Computer Interaction (Grade A)}
\begin{itemize}
    \item Received world-class education in UX/UI design principles, applying eye-tracking data and heatmaps to analyse user attention patterns and create clean, intuitive interfaces for optimal user engagement in digital applications.
\end{itemize}

\textbf{Previous Schooling}
\begin{itemize}
    \item A Levels: Maths (A*), Further Maths (A*), Business (B), Accounting (B)
\end{itemize}

% Software Projects
\section*{SOFTWARE PROJECTS}

\textbf{Co-Founder \& CTO}, \href{https://www.arcadeus.io}{Arcadeus} \hfill \textit{2025 May-Present}
\begin{itemize}
    \item Developed an LLM-powered real estate analysis tool using LangGraph, seamlessly integrated with Microsoft Excel via Office.js to process live spreadsheet data. Architected and built the complete technical infrastructure independently.
    \item Established partnerships with leading academic institutions including University of Cambridge and Bayes Business School
    \item Guest lectured for Cambridge MSc Real Estate Finance program on AI applications in real estate transactions
\end{itemize}

\textbf{Founder \& CEO}, Frift -- Student Marketplace \hfill \textit{2024 Sep-Present}
\begin{itemize}
    \item Designed and launched a cross-platform marketplace app for iOS and Android with a unified Firebase backend
    \item Built scalable real-time data architecture with Firebase/Firestore and custom Cloud Functions for user verification, automated moderation, and multi-tag filtering. Optimised performance by bundling frequently-accessed static data into a single JSON asset, reducing from 200+ individual Firebase queries to 1 local read for faster load times and lower operational costs.
    \item Delivered a polished, engaging user experience with social-inspired feeds, responsive product grids, and optimised media handling, boosting engagement and session time.
\end{itemize}

\textbf{Web-design Lead}, Marvellous Maps, Bath, UK \hfill \textit{2025 Feb-2025 May}
\begin{itemize}
    \item Lead and directed the project of a \$1,000,000/yr online store in their move from Squarespace to Shopify.
\end{itemize}

% Professional Experience
\section*{PROFESSIONAL EXPERIENCE}

\textbf{180 Degrees Consulting}, Bath, UK \hfill \textit{2024 Feb-2024 Jun}\\
\textit{Consultant}
\begin{itemize}
    \item Developed effective footfall strategies for the Soldiers of Gloucestershire Museum, along with the partnership with Oliver Wyman, by conducting comprehensive primary and secondary market research, analysing 50+ national competitors.
    \item Excellent data visualisation and story-telling capabilities by creating compelling PowerPoint presentations using ThinkCell.
    \item Weekly meetings with the board of directors to pitch strategic recommendations that consistently exceeded their expectations.
\end{itemize}

\textbf{SOBIC}, Bath, UK \hfill \textit{2024 Feb-2024 May}\\
\textit{Global Markets Researcher}
\begin{itemize}
    \item Delivered a persuasive asset pitch for NYSE: CVS to a group of investors backed by calculating DCF and LBO using Excel.
    \item Published research papers based on recent events such as interest rates in Japan, and crude fluctuations due to the Israeli war.
\end{itemize}

\textbf{Dreamfora}, Seoul, South Korea \hfill \textit{2023 Jun-2023 Aug}\\
\textit{Marketing Summer Intern}
\begin{itemize}
    \item Leveraged the company's demographic data and analysed competitors to develop a tailored and proven marketing strategy.
    \item Successfully pitched the idea to the CEO with a detailed cost breakdown and executed the strategy with the allocated funds.
    \item Produced 20 promotional videos and grew the Instagram following from 0 to 8,900 within 11 weeks.
    \item Adapted to and thrived in an international work environment, showcasing cultural fluency, adeptness in cross-cultural communication, and a keen ability to navigate diverse perspectives.
\end{itemize}

% Technical Skills & Achievements
\section*{TECHNICAL SKILLS \& ACHIEVEMENTS}

\begin{itemize}
    \item \textbf{Programming \& Data:} Python, SQL, MATLAB, R, SPSS; Expert in Excel (financial modelling), PowerPoint (ThinkCell visualisations).
    \item \textbf{Software/Tools:} Javascript, Flutter/Dart, Firebase/Firestore, LangGraph, Office.js.
    \item \textbf{Achievements:} Gold Scholarship (£5,000/year, top 50 recipients); Won \$7,000+ in esports competitions, honing high-pressure teamwork.
\end{itemize}

\end{document}
